Portfolios of Subgraph Isomorphism Algorithms

### 2015-12-09 paper/paper.tex
more experimental setup

>>>>

We use 10-fold cross-validation to determine the performance of the LLAMA
models. The entire set of instances was randomly partitioned into 10 subsets of
approximately equal size. Of the 10 subsets, 9 were combined to form the
training set for the algorithm selection models, which were evaluated on the
remaining subset. This process was repeated 10 times for all possible
combinations of training and test sets. At the end of this process, each problem
instance in the original set was used exactly once to evaluate the performance
of the algorithm selection models.
